---
title: "2021 Fantasy Football Season Running Back Analysis"
author: "Siddharth V"
date: "2022-08-28"
output: html_document
---

## The 2021 Fantasy Football Season
Ahhh fantasy football. The most stressful, yet fun activity in many people's lives. So many players drafted, some surprised, and some disappointed. In this post, let's take a look at how the most important position in fantasy football, running backs, performed during the 2021 season, and if there are any useful trends present that can help us draft better in the future. 

## Load in the appropriate libraries
```{r}
library(tidyverse)
library(htmltools)
library(rvest)
library(lubridate)
```

## Bring in the data
```{r}
## Create a url for the fantasy season
fantasy_url <- read_html('https://www.pro-football-reference.com/years/2021/fantasy.htm') 
## Convert the url info into a list
fantasy_lst = fantasy_url %>%
  html_nodes('#fantasy') %>%
  html_table()

## Create a temporary data frame to hold the data from the info list
temp_fantasy_df = fantasy_lst[[1]]
```

## Clean the data
```{r}
## Remove the headings from the data frame
colnames(temp_fantasy_df) = temp_fantasy_df[1,]

## Change the column names so that the data frame can be modified
colnames(temp_fantasy_df)[c(9,10,11,13,14,16,19,21,24)] = c("pass_att","pass_yds","pass_td","rush_att","rush_yds","rush_tds","rec_yds","rec_tds","total_tds")

## Remove the first row with redundant column names 
mod1_fantasy_df = temp_fantasy_df %>%
  filter(Rk != "Rk")

## Remove the Rk column and values in the Tm column that are 2TM and 3TM
mod2_fantasy_df = mod1_fantasy_df %>%
  select(-"Rk") %>%
  filter(Tm != "2TM" & Tm != "3TM")

## Fill in the blank values with NAs so that they can be removed at a later time
mod2_fantasy_df[mod2_fantasy_df==""] <- NA
```

