---
title: "An Interview Test Part 3"
author: "Siddharth V"
date: '2022-04-29'
output: html_document
---

## Q13. Using the data frame from question 11 and consider only freshmen 2nd exam scores (Hint: investigate the assignment_id variable) and implement One-Way ANOVA in which you would like to determine if the populations means of performance on the exam (numeric_grade) are the same across major. Answer the following questions to be able to fully grasp the material.

## Load in the data and the libraries
```{r}
library(readr)
library(tidyverse)
grades_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/grades.csv'
assignments_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/assignments.csv' 
students_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/students.csv'
grades_df = read_csv(url(grades_url))
assignments_df = read_csv(url(assignments_url))
students_df = read_csv(url(students_url))
```

## Part A: Create the data frame that will allow you to answer the statistical question.
```{r}
freshman_exam2_df = student_performance_df %>%
  filter(assignment_id == 20,
         student_level == '1-Freshmen')
```

## Part B: What is the explanatory and response variables?
The explanatory variable is the major type and the response variable is the numeric grade.
