---
title: "An Interview Test Part 2"
author: "Siddharth V"
date: '2022-04-27'
output: html_document
---

## Load in the data and the libraries
```{r}
library(readr)
library(tidyverse)
grades_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/grades.csv'
assignments_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/assignments.csv' 
students_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/students.csv'
grades_df = read_csv(url(grades_url))
assignments_df = read_csv(url(assignments_url))
students_df = read_csv(url(students_url))
```

## Question 7: Join the students data frame with grades data frame. Save this data frame with appropriate an appropriate name.
```{r}
student_grade_df = inner_join(students_df, grades_df, by = 'student_id')
```

## Question 8: Of the English majors, who performed the worst on assignment 1?
```{r}
english_major_df = student_grade_df %>%
  subset(assignment_id == 1)
```
Matthew performed the worst on assignment 1, with a grade of 4.

## Question 9: Which assignment did the junior engineer students performed the best on average using their average numeric grade?
```{r}
average_grade_assignment_df = student_grade_df %>%
  group_by(assignment_id, student_level, major) %>%
  summarise_at(vars(numeric_grade), list(mean_score = mean)) 

mod1_average_grade_assignment_df = ungroup(average_grade_assignment_df)

junior_engineer_df = mod1_average_grade_assignment_df %>%
  filter(major == 'Engineering',
         student_level == '3-Junior')
```
The junior engineer students performed best on assignment 20 with an average grade of 76.214286.

## Questioin 10: Which student level performed the best as Statistics and Mathematics major using all their assignments average numeric grade?
```{r}
mod2_average_grade_df = student_grade_df %>%
  group_by(student_level, major) %>%
  summarise_at(vars(numeric_grade), list(mean_assignment_grade = mean)) 

average_student_grade_df = ungroup(mod2_average_grade_df)
```
Sophomores performed best as Statistics and Math majors with an average numeric grade of 17.63333.

## Question 11: Join the data frame from question 7 to the assignment data frame. Save this data frame with appropriate an appropriate name.
```{r}
student_performance_df = inner_join(student_grade_df, assignments_df, by = 'assignment_id')
```

