---
title: "An Interview Test Part 3"
author: "Siddharth V"
date: '2022-04-29'
output: html_document
---

## Q13. Using the data frame from question 11 and consider only freshmen 2nd exam scores (Hint: investigate the assignment_id variable) and implement One-Way ANOVA in which you would like to determine if the populations means of performance on the exam (numeric_grade) are the same across major. Answer the following questions to be able to fully grasp the material.

## Load in the data and the libraries
```{r}
library(readr)
library(tidyverse)
grades_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/grades.csv'
assignments_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/assignments.csv' 
students_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/students.csv'
grades_df = read_csv(url(grades_url))
assignments_df = read_csv(url(assignments_url))
students_df = read_csv(url(students_url))
```

## Part A: Create the data frame that will allow you to answer the statistical question.
```{r}
freshman_exam2_df = student_performance_df %>%
  filter(assignment_id == 20,
         student_level == '1-Freshmen')
```

## Part B: What is the explanatory and response variables?
The explanatory variable is the major type and the response variable is the numeric grade.

## Part C: Write the null and alternative hypotheses?
Null: The type of major a freshman has does not impact their numeric grade on exam 2.
Alternative: The type of major a freshman has does impact their numeric grade on exam 2.

## Part D: Summarize (Hint: find sample size, mean, standard deviation) and Visualize Data (Hint: box plot and make it look professional).
```{r}
## Summary of freshman_exam2_df 
summary_freshman_exam2_df = freshman_exam2_df %>% 
  group_by(major) %>% 
  summarise(sample_size = n(),
            mean_score = mean(numeric_grade ,na.rm = TRUE),
            sd_score = sd(numeric_grade ,na.rm = TRUE))
```

```{r}
## Box plot of data
freshman_exam2_df %>%  
  ggplot(aes(x = major, y = numeric_grade)) +
  geom_boxplot() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Major', y = 'Score on Second Exam', title = 'Box Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```

