---
title: "Exploring One-Way Anova Part I"
author: "Siddharth V"
date: '2022-04-04'
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
library(htmltools)
```

## Question 1: Create an example when it would be appropriate to implement One-Way ANOVA.
  A sports shoe company is comparing how high athletes can jump when wearing a new model of their shoe compared to the old model of the same shoe.
  
## Question 2: State the null the alternative hypotheses for the example that you came up with for your example in question 1.
  Null Hypothesis: When wearing the new model of the shoe, athletes won't see an increase in the height they are able to jump up to.
  
  Alternative Hypothesis: When wearing the new model of the shoe, athletes will be able to jump to a higher height. 
  
## Question 3: State the null the alternative hypotheses based on these variables.
  Null Hypothesis: There is no change in points per game over the different positions.
  
  Alternative Hypothesis: There is a change in points per game over the different positions.
```{r}
## Creating a url for Jordan's career
mj_url <- read_html('https://www.basketball-reference.com/leagues/NBA_1991_per_game.html')

## Turning that information into a list
mj_info_lst = mj_url %>%
  html_nodes('#per_game_stats') %>%
  html_table()

## Creating a temporary data frame to hold the information from the list
temp_mj_df = mj_info_lst[[1]]

## Filtering out the season where he first won the championship and making that the lj data frame
mj_df_without_name = temp_mj_df %>%
  filter(Rk != 'Rk') %>%
  mutate_if(~any(str_detect(string = ., pattern = '^-?[0-9]\\d*(\\.\\d+)?$')),
            ~ as.numeric(.)) %>%
  distinct(Player,max(G),.keep_all = TRUE)

## Fixing column names
colnames(mj_df_without_name)[c(11,14,17,18,21)] = c('FG_percent', '3P_percent', '2P_percent', 'eFG_percent', 'FT_percent')

## Adding a column with the data frame name
mj_df = mj_df_without_name %>%
  mutate(df_name = 'MJ')
```

## Creating a box plot for the data
```{r}
mj_df %>%  
  ggplot(aes(x = Pos, y = PTS)) +
  geom_boxplot() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Position', y = 'Points Averaged', title = 'Box Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```
## This graph is a box plot of the positions listed in the Michael Jordan data frame plotted along with the points averaged by those players at the positions in the data frame. The red dots represent the mean points averaged at each position.

## Creating a violin plot for the data
```{r}
mj_df %>%  
  ggplot(aes(x = Pos, y = PTS)) +
  geom_violin() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Position', y = 'Points Averaged', title = 'Violin Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))

```
## This graph is a violin plot that plots the position against the points averaged with all the players in the season where Michael Jordan won his first championship. The red dot represents the mean points averaged among positions. Most of the data across the positions is concentrated in the single digits, and the position where the data is most spread out is small forward, or SF.

## Summarization of the Data
```{r}
summary_mj_df = mj_df %>% 
  group_by(Pos) %>% 
  summarise(sample_size = n(),
            mean_pts = mean(PTS,na.rm = TRUE),
            sd_pts = sd(PTS,na.rm = TRUE))

summary_mj_df
```

## Summary Notes
  The sample size is not equal across positions
  Since SF-SG and SG-SF only had one entry in the data frame, there was no standard deviation
  The mean points averaged per game is greatest for SF during the year where MJ won his first championship
  PF has the greatest sample size among all the positions
  While SF has the largest mean points averaged, it also has the greatest sd points averaged, which shows that the data is very spread out
  
  
## Question 1: What does mean measure with the sample? the center or variability? Explain.
  The mean measures the center of the sample, because it uses all of the data provided and tries to find the value that is closest to the middle of the entire data set.
  
## Question 2: What does standard deviation measure within the sample? the center or variability? Explain.
  The standard deviation measures the variability within the sample, because it looks at all of the data points in the sample and then assesses the distance of each point from the mean and then finds the average distance.
  
  


  

