---
title: "Exploring One-Way Anova Part I"
author: "Siddharth V"
date: '2022-04-04'
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
library(htmltools)
```

## Question 1
  A sports shoe company is comparing how high athletes can jump when wearing a new model of their shoe compared to the old model of the same shoe.
  
## Question 2
  Null Hypothesis: When wearing the new model of the shoe, athletes won't see an increase in the height they are able to jump up to.
  
  Alternative Hypothesis: When wearing the new model of the shoe, athletes will be able to jump to a higher height. 
  
## Question 3
  Null Hypothesis: There is no change in points per game over the different positions.
  
  Alternative Hypothesis: There is a change in points per game over the different positions.
```{r}
## Creating a url for Jordan's career
mj_url <- read_html('https://www.basketball-reference.com/leagues/NBA_1991_per_game.html')

## Turning that information into a list
mj_info_lst = mj_url %>%
  html_nodes('#per_game_stats') %>%
  html_table()

## Creating a temporary data frame to hold the information from the list
temp_mj_df = mj_info_lst[[1]]

## Filtering out the season where he first won the championship and making that the lj data frame
mj_df_without_name = temp_mj_df %>%
  filter(Rk != 'Rk') %>%
  mutate_if(~any(str_detect(string = ., pattern = '^-?[0-9]\\d*(\\.\\d+)?$')),
            ~ as.numeric(.)) %>%
  distinct(Player,max(G),.keep_all = TRUE)

## Fixing column names
colnames(mj_df_without_name)[c(11,14,17,18,21)] = c('FG_percent', '3P_percent', '2P_percent', 'eFG_percent', 'FT_percent')

## Adding a column with the data frame name
mj_df = mj_df_without_name %>%
  mutate(df_name = 'MJ')
```

