---
title: "Exploring One-Way Anova Part I"
author: "Siddharth V"
date: '2022-04-04'
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
library(htmltools)
```

## Question 1
  A sports shoe company is comparing how high athletes can jump when wearing a new model of their shoe compared to the old model of the same shoe.
  
## Question 2
  Null Hypothesis: When wearing the new model of the shoe, athletes won't see an increase in the height they are able to jump up to.
  
  Alternative Hypothesis: When wearing the new model of the shoe, athletes will be able to jump to a higher height. 
  
## Question 3
  Null Hypothesis: There is no change in points per game over the different positions.
  
  Alternative Hypothesis: There is a change in points per game over the different positions.
```{r}
## Creating a url for Jordan's career
mj_url <- read_html('https://www.basketball-reference.com/leagues/NBA_1991_per_game.html')

## Turning that information into a list
mj_info_lst = mj_url %>%
  html_nodes('#per_game_stats') %>%
  html_table()

## Creating a temporary data frame to hold the information from the list
temp_mj_df = mj_info_lst[[1]]

## Filtering out the season where he first won the championship and making that the lj data frame
mj_df_without_name = temp_mj_df %>%
  filter(Rk != 'Rk') %>%
  mutate_if(~any(str_detect(string = ., pattern = '^-?[0-9]\\d*(\\.\\d+)?$')),
            ~ as.numeric(.)) %>%
  distinct(Player,max(G),.keep_all = TRUE)

## Fixing column names
colnames(mj_df_without_name)[c(11,14,17,18,21)] = c('FG_percent', '3P_percent', '2P_percent', 'eFG_percent', 'FT_percent')

## Adding a column with the data frame name
mj_df = mj_df_without_name %>%
  mutate(df_name = 'MJ')
```

## Creating a box plot for the data
```{r}
mj_df %>%  
  ggplot(aes(x = Pos, y = PTS)) +
  geom_boxplot() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Position', y = 'Points Averaged', title = 'Box Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```
## This graph is a box plot of the positions listed in the Michael Jordan data frame plotted along with the points averaged by those players at the positions in the data frame. The red dots represent the mean points averaged at each position.

## Creating a violin plot for the data
```{r}
mj_df %>%  
  ggplot(aes(x = Pos, y = PTS)) +
  geom_violin() +
  stat_summary(fun ="mean", color = 'red')+
  labs(x = 'Position', y = 'Points Averaged', title = 'Violin Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))

```
## This graph is a violin plot that plots the position against the points averaged with all the players in the season where Michael Jordan won his first championship. The red dot represents the mean points averaged among positions. Most of the data across the positions is concentrated in the single digits, and the position where the data is most spread out is small forward, or SF.

## Summarization of the Data
```{r}
summary_mj_df = mj_df %>% 
  group_by(Pos) %>% 
  summarise(sample_size = n(),
            mean_pts = mean(PTS,na.rm = TRUE),
            sd_pts = sd(PTS,na.rm = TRUE))

summary_mj_df
```



