---
title: "Phoenix Suns Regular Season Analysis"
author: "Siddharth V"
date: '2022-05-22'
output: html_document
---

## Some Context
The Phoenix Suns had a remarkable regular season this year, and although it ended in disappointment in the playoffs, that should not take away from the sucess that the team from the valley had during the regular season. The Suns won a franchise record 64 games this year and were owners of the NBA's best record and the first seed in the Western Conference. Let's take a look at some of the trends that can be observed from this season by the Suns. 

## Load in the appropriate libraries
```{r}
library(tidyverse)
library(htmltools)
library(rvest)
```

## Bring in the data 
```{r}
## Create a URL for the Phoenix Suns 2021-22 season
suns_url <- read_html("https://www.basketball-reference.com/teams/PHO/2022/gamelog/")

## Convert the information in the URL into a list
suns_info_lst = suns_url %>%
  html_nodes("#tgl_basic") %>%
  html_table()

## Create a temporary data frame to hold the data from the info list
temp_suns_df = suns_info_lst[[1]]

## Clean the data
## Start by removing team and opponent from the column names
colnames(temp_suns_df) = temp_suns_df[1,]

## Make the team and oppenent stats discernable in the column names
colnames(temp_suns_df)[c(4,7,8,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41)] = c("game_location","Tm_Score","Opp_Score","Opp_FG","Opp_FGA","Opp_FG%","Opp_3P","Opp_3PA","Opp_3P%","Opp_FT","Opp_FTA","Opp_FT%","Opp_ORB","Opp_TRB","Opp_AST","Opp_STL","Opp_BLK","Opp_TOV","Opp_PF")

## Remove Rk
mod1_temp_suns_df = temp_suns_df %>%
  filter(Rk != "Rk")
```


