---
title: "Two Way Anova Part 1"
author: "Siddharth V"
date: '2022-04-13'
output: html_document
---

```{r}
library(tidyverse)
library(ggpubr)
```

## The purpose of Two-Way ANOVA
The primary purpose of two-way another is to determine if two explanatory variables have an impact on a response variable, in other words, are the means the same across each level of an explanatory variables as well the interaction of the explanatory variables on the response. It works in a very subtle way, so lets use the mtcars data frame to make sense of this technique. Let’s say we want to know whether the means of miles per gallon are the same across the levels of cylinders (4, 6, 8) as well as the the means of miles per gallon across the transmission types (i.e., manual and automatic).

Example 1: A farmer has three types of fertilizer and four types of corn. She wants to determine whether the three types of fertilizer and four types of corn has the same impact on her crop yield. They are three questions that she could ask:

Is the population mean of crop yield the same for each fertilizer?
Is the population mean of crop yield the same for each type of corn?
Is there an interaction effect on crop yield between fertilizer and corn type?

Example 2: Does the type of drink (red bull, coffee, orange juice or water) or type of food (donuts or eggs) before a 10K have an impact on finishing time? Again, there are now three questions that can be asked:

Determine whether the population mean of finishing time of the 10K the same for these four drinks.
Determine whether the population mean of finishing time of the 10K the same for the two types of food.
Determine whether there is an interaction effect between food and drink types on the 10K finishing time.

## What do these two examples have in common?
- There are 3 variables
- One variable is quantitative and the other two are categorical or categorical binary

## Question 1: Create an example when it would be appropriate to implement Two-Way ANOVA. State the variables, their types (i.e., categorical “binary” or quantitative), and which are the explanatory variables and response variable.
A student is studying for her finals exam in a few weeks. She wants to know whether the 5 types of flashcards she uses or the 3 types of textbooks she uses will have an effect on her test score. In this example, the types of flashcards and textbooks are the categorical variables, while the test score is the quantitative variable. The explanatory variables are the textbook and flashcard types and the response variable is the test score. 

## Hypothesis Testing
The null hypothesis for Two-Way ANOVA is that the population means are equal across both explanatory variables. On the other hand, the alternative hypothesis for One-Way ANOVA is the complement of the null hypothesis which is that at least one of the population means is different from the others.

## Question 2: State the null the alternative hypotheses for the example that you came up with for your example in question 1.
Null: The population means of test scores are the same across flashcard type.
Alternative: The population means of test scores are not the same across flashcard type.

## The general idea is to acquire a sample from the population and use the evidence from the sample to either reject the claim (the null hypothesis) or not reject the claim (the null hypothesis).

## Creating and manipulating the MJ data frame
```{r}
## Creating a url for Jordan's career
mj_url <- read_html('https://www.basketball-reference.com/leagues/NBA_1991_per_game.html')

## Turning that information into a list
mj_info_lst = mj_url %>%
  html_nodes('#per_game_stats') %>%
  html_table()

## Creating a temporary data frame to hold the information from the list
temp_mj_df = mj_info_lst[[1]]

## Filtering out the season where he first won the championship and making that the lj data frame
mj_df_without_name = temp_mj_df %>%
  filter(Rk != 'Rk') %>%
  mutate_if(~any(str_detect(string = ., pattern = '^-?[0-9]\\d*(\\.\\d+)?$')),
            ~ as.numeric(.)) %>%
  distinct(Player,max(G),.keep_all = TRUE)

## Fixing column names
colnames(mj_df_without_name)[c(11,14,17,18,21)] = c('FG_percent', '3P_percent', '2P_percent', 'eFG_percent', 'FT_percent')

## Adding a column with the data frame name
mj_df = mj_df_without_name %>%
  mutate(df_name = 'MJ')

## Adding a new variable called binary_mp
mod1_mj_df = mj_df %>%
  mutate(binary_mp = case_when(
    MP < 20 ~ 'few_mp',
    MP >= 20 ~ 'large_mp'
  ))
```

## Question 3: State the null the alternative hypotheses based on these variables for your data set.
Null: The population means of points scored is same across all positions.
Alternative: The population means of points scored is not the same across all positions. 

Null: The population means of points scored is the same whether few minutes or many minutes are played.
Alternative: The population means of points scored is not the same whether few minutes or many minutes are played.

Null: There is not an interaction effect between minutes played and position.
Alternative: There is an interaction effect between minutes played and position.





